**Density Dependence**

### 2023-03-09 Rmd/report mac.Rmd
added refpoints

---
output:
  word_document:
    reference_docx: ../report_template.dotx
mathjax: TRUE
bibliography: refs.bib
---

@@

>>>>

---
output:
  word_document:
    reference_docx: ../report_template_v1.1.dotx
mathjax: TRUE
bibliography: refs.bib
---

@@

**Reference points**

Reference points estimated for the different scenarios are in the table below.

tab_nums(
  name    = "refpoints", level = 1, display = FALSE,
  caption = paste0(mystkname, ". Reference points for the different scenarios"))

cat(readLines(file.path(tablesdir, paste(section,mystk, "refpoints.txt", sep="_"))), sep = '\n')

*`r tab_nums("refpoints")`*
